---
title: "Gradethis demo"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
# editor_options:
#   preview: viewer
description: "Learn how to use gradethis to provide automated, personalized, formative feedback to student answers in learnr tutorials."
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
gradethis_setup()
knitr::opts_chunk$set(echo = FALSE)
```

## Welcome

###

The `gradethis` package provides three ways to autocheck student code in [learnr](https://rstudio.github.io/learnr/) tutorials. You can use:

1. `grade_result()` to check that the student's code returns a correct _result_.
1. `grade_result_strict()` to check that the student's code returns a _result_ that satisfies a complete set of conditions. This is akin to unit testing the result.
1. `grade_code()` to check that the student's _code_ exactly matches the solution code.

You can also use gradethis to create your own customized checking code.

### Syntax

In each case, you grade an exercise by passing a `gradethis` function to the `-check` code chunk associated with the exercise. This code chunk will share the same label root as the exercise code chunk, but the root will be suffixed with `-check`. 

See the [learnr documentation](https://rstudio.github.io/learnr/exercises.html) to learn more about code chunks in learnr tutorials.

### 

Here is how an example exercise and `-check` chunk would appear in a learnr document.

````markdown
`r ''````{r exercise_1, exercise = TRUE}
x + 1
```

`r ''````{r exercise_1-check}
grade_result(
  pass_if(~ identical(.result, 2), "Good job!")
)
```
````

### Goal

`gradethis` functions are designed to provide formative feedback to the student. When a student clicks "Submit Answer" in his or her learnr tutorial, the `gradethis` function immediately performs three tasks. It:

1. Displays whether or not the answer is correct
1. Returns an instructional message customized to the student's submission
1. Offers dynamically generated encouragement

`gradethis` does not itself calculate a final grade for the student. 

### Setup

To use `gradethis` inside a [learnr](https://rstudio.github.io/learnr/) tutorial, we suggest calling `gradethis::gradethis_setup()` inside the tutorial's `setup` chunk. This is how it will look in the learnr R Markdown file:

````markdown
`r ''````{r setup}
library(gradethis)
gradethis_setup()
```
````

You can also see this in the first code chunk of the .Rmd file associated with this tutorial.

### 

The remainder of this document looks at how to use individual `gradethis` functions.

## `grade_result()`

###

`grade_result()` checks whether or not the student's code returns the correct result. It matches the result against one or more conditions and returns the message (and correct/incorrect status) associated with the first matched condition.

Here is an example of `grade_result()` in use.

* Calculate the average number of weeks in a month.

```{r grade_res, exercise = TRUE}

```

```{r grade_res-check}
grade_result(
  pass_if(~ identical(.result, 365.25 / 12 / 7), "There are 4.348214 weeks on average in a month."),
  fail_if(~ identical(.result, 365 / 7 / 12), "Did you assume the average year has 365 days? Due to leap years, the average year actually has 365.25 days."),
  fail_if(~ identical(.result, 52 / 12), "Did you assume that the average year has 52 weeks? It is actually has a little more because 52 * 7 is only 364 days."),
  fail_if(~ identical(.result, 4), "Close, but four is the average number of whole weeks in a month."),
  fail_if(~ TRUE, "Not quite. Consider that there are 365.25 days in an average year, 12 months in a year, and 7 days in a week.")
)
```


### 

And here is the code behind the example.

````markdown
`r ''````{r grade_result, exercise = TRUE}

```

`r ''````{r grade_result-check}
grade_result(
  pass_if(~ identical(.result, 365.25 / 12 / 7), "There are 4.348214 weeks on average in a month."),
  fail_if(~ identical(.result, 365 / 7 / 12), "Did you assume the average year has 365 days? Due to leap years, the average year actually has 365.25 days."),
  fail_if(~ identical(.result, 52 / 12), "Did you assume that the average year has 52 weeks? It is actually has a little more because 52 * 7 is only 364 days."),
  fail_if(~ identical(.result, 4), "Close, but four is the average number of whole weeks in a month."),
  fail_if(~ TRUE, "Not quite. Consider that there are 365.25 days in an average year, 12 months in a year, and 7 days in a week.")
)
```
````

### Syntax

`grade_result()` should contain a sequence of `fail_if()` and `pass_if()` functions.

Each `fail_if()` and `pass_if()` function should contain:

1. A logical test prefixed by a `~` 
1. A character string to display if the logical test evaluates to true

Use `.result` to refer to the student's answer within the logical tests.

### Execution

`grade_result()` will evaluate the `_if` functions in order, replacing `.result` with the student's result as it does. 

`grade_result()` will stop and return the message of the first `_if` function whose condition evaluates to true. If that function is: 

* `pass_if()`, the exercise will be marked correct 
* `fail_if()`, the exercise will be marked wrong

Order matters! `grade_result()` will not continue to evaluate `_if()` functions after one returns a message.

### Choose the best grading function for you

`grade_result()` will mark a result correct if it passes a _single_ `pass_if()` statement (without first triggering a `fail_if()`). 

If you would like to ensure that a result satisfies _every_ `pass_if` statement use `grade_result_strict()`.

### 

`grade_result()` will not check the students code. Nor will `grade_result()` know if the student directly typed the correct result into the exercise box.

If you want to check the code the student used to get a result, use `grade_code()`

###

See `?grade_result` for more information.

## `grade_result_strict()`

### 

`grade_result_strict()` is similar to `grade_result()`, but it requires a result to pass _every_ `pass_if()` function contained in its function body. This method is analogous to creating unit tests that all need to pass.

Here is an example of `grade_result_strict()` in use:

Please make a function in the exercise space below, but do not assign the function to an object.  The function should:

* Take a single `x` argument
* Add the integer `1` to the `x` value.

Then click Submit Answer.

```{r grade_cond, exercise = TRUE}
function(x) {
  # solution is x + 1L
  x + 1
}
```

```{r grade_cond-check}
grade_result_strict(
  pass_if(~ .result(3) == 4),
  pass_if(~ identical(.result(0), 1)),
  pass_if(~ identical(sapply(1:10, .result), 2:11)),
  pass_if(~ sapply(1:10, .result) == 2:11),
  pass_if(~ all.equal(sapply(1:10, .result), 2:11)),
  pass_if(~ checkmate::test_function(.result, args = c("x")))
)
```

### 

And here is the code behind the example.

````markdown
`r ''````{r grade_result_strict, exercise = TRUE}
function(x) {
  # solution is x + 1L
  x + 1
}
```

`r ''````{r grade_result_strict-check}
grade_result_strict(
  pass_if(~ .result(3) == 4),
  pass_if(~ identical(.result(0), 1)),
  pass_if(~ identical(sapply(1:10, .result), 2:11)),
  pass_if(~ sapply(1:10, .result) == 2:11),
  pass_if(~ all.equal(sapply(1:10, .result), 2:11)),
  pass_if(~ checkmate::test_function(.result, args = c("x")))
)
```
````

### Syntax

`grade_result_strict()` takes a set of `pass_if()` functions. Each `pass_if()` function should contain:

1. a logical test prefixed by a `~` 

Use `.result` to refer to the student's answer within the logical tests.

### Evaluation

`grade_result_strict()` will mark a result as correct only if passes every `pass_if()` statement. This is especially useful for grading function definitions.

### 

See `?grade_result_strict` for more information.

## `grade_code()`

### 

`grade_code()` to checks whether the student code matches the solution code. If the code does not match, `grade_code()` will tell the student exactly where their code begins to diverge from the solution and how to get back on track. Here's an example:

* Take the square root of the log of 2, then click Submit Answer.

```{r grade_code, exercise = TRUE}

```

```{r grade_code-solution}
sqrt(log(2))
```

```{r grade_code-check}
grade_code("Don't worry, things will soon get harder.")
```

We can also provide a more specific feedback when we expect an assign statement, for example.

* The expected here is `a <- sample(1:6, size = 1)`. Enter 123, then click Submit Answer.

```{r grade_code_assign, exercise = TRUE}

```

```{r grade_code_assign-solution}
a <- sample(1:6, size = 1)
```

```{r grade_code_assign-check}
grade_code("Don't worry, things will soon get harder.")
```

You should see a red box with "I expected you to assign something to something else with <- where you wrote 123."

## Grading exercise errors

Since `gradethis_setup()` sets `learnr::tutorial_options(exercise.error.check.code = "gradethis::grade_code()")`, when an exercise submission produces an evaluation error, intelligent feedback is provided via `grade_code()` (when a solution is provided). Try it yourself by submitting `mt` (R error, incorrect answer), then `cars` (No error, incorrect answer), then `mtcars` (correct answer) below:

```{r mtcars, exercise = TRUE}

```

```{r mtcars-solution}
mtcars
```

```{r mtcars-check}
grade_result(
  fail_if(~identical(.result, cars), "This is the cars (not mtcars) dataset."),
  pass_if(~identical(.result, mtcars))
)
```

### 

And here is the code behind the example.

````markdown
`r ''````{r mtcars, exercise = TRUE}

```

`r ''````{r mtcars-solution}
mtcars
```

`r ''````{r mtcars-check}
grade_result(
  fail_if(~identical(.result, cars), "This is the cars (not mtcars) dataset."),
  pass_if(~identical(.result, mtcars))
)
```
````

### 

In the case that you wish to provide custom checking logic for errors, you can also provide a `-error-check` chunk. If the student submission generates an error, gradethis will run the checking code in the `-error-check` chunk instead of the checking code in the `-check` chunk. gradethis will only run the `-error-check` code if the student submission generates an error. 


```{r mtcars2, exercise = TRUE}

```

```{r mtcars2-solution}
mtcars
```

```{r mtcars2-error-check}
grade_code(incorrect = "This code produces an error (press 'Run Code' to see it).", glue_incorrect = "{ .message } { .incorrect }")
```

```{r mtcars2-check}
grade_result(
  fail_if(~identical(.result, cars), "This is the cars (not mtcars) dataset."),
  pass_if(~identical(.result, mtcars))
)
```

And here is the code behind the example.

````markdown
`r ''````{r mtcars2, exercise = TRUE}

```

`r ''````{r mtcars2-solution}
mtcars
```

`r ''````{r mtcars2-error-check}
grade_code(incorrect = "This code produces an error (press 'Run Code' to see it).", glue_incorrect = "{ .message } { .incorrect }")
```

`r ''````{r mtcars2-check}
grade_result(
  fail_if(~identical(.result, cars), "This is the cars (not mtcars) dataset."),
  pass_if(~identical(.result, mtcars))
)
```
````

### Syntax

`grade_code()` requires a model solution to compare student code to. Supply this solution in a learnr `-solution` chunk, i.e. a chunk whose label is the label of the exercise it is associated with followed by `-solution`: 

````markdown
`r ''````{r grade_code-solution}
sqrt(log(2))
```
````

### 

`grade_code()` will compare the last expression in the student submission to the last expression in the solution chunk.

Teachers will usually pass `grade_code()` a character string to display to the student if their code successfully matches the solutiuon, e.g.

```r
grade_code("Good job. Don't worry, things will soon get harder.")
```

### Execution

`grade_code()` does not check the result of the student's code. 

Instead, `grade_code()` parses the student code into a call tree. As it does, it standardizes argument names and accounts for the presence of pipes (`%>%`). 

`grade_code()` then does the same for the solution code. 

Finally, `grade_code()` recursively walks the two call trees. 

### 

`grade_code()` stops and returns a message if the student code:

1. **contains malformed code** that would cause an error if passed to `match.call()`
1. **contains a different element** than the solution
1. **contains an extra element** that is not in the solution
1. **is missing an element** that appears in the solution

If none of the above occurs, `grade_code()` marks the answer as correct.

### Feedback

`grade_code()` attempts to supply helpful feedback that makes sense to the student without giving away the solution. To do this, `grade_code()` messages take the form of 

> "I expected X, where you wrote Y. Please try again." 

Here Y may be an argument or function call that appears at the beginning, end, or middle of the student code. 

`grade_code()` will catch mistakes one at a time in the order that they appear in the students code. This lets the student iteratively improve their code.

### 

See `?grade_code` for more information.


## Custom Checking Code

### 

`gradethis` can accept any checking method that returns a `gradethis::graded` object.

The example below returns a correct/incorrect answer with 50/50 probability.


````markdown
`r ''````{r custom, exercise = TRUE}
"Flip a coin"
```

`r ''````{r custom-check}
fifty_fifty_checker <- function(
  correct = "Correct!",
  incorrect = "May the odds be ever in your favor!",
  ...,
  user
) {
  is_correct <- (runif(1) < 0.5)
  gradethis::graded(
    correct = is_correct,
    message = ifelse(is_correct, correct, incorrect)
  )
}
fifty_fifty_checker()
```
````

### Syntax

The custom checking function should return the output of `gradethis::graded()` which takes two arguments:

1. `correct` - `TRUE` is the answer is correct, `FALSE` otherwise
1. `message` - an optional character string to display to the student

### Evaluation

To use the custom checking function, place it in an exercise `-check` chunk, as you would place `grade_result()`, `grade_result_strict()`, or `grade_code()`.

### Try it!

---------------------------

Are you feeling lucky?

If you are, click Submit Answer.

```{r custom, exercise = TRUE}
"Flip a coin"
```

```{r custom-check}
fifty_fifty_checker <- function(
  correct = "Correct!",
  incorrect = "May the odds be ever in your favor!",
  ...,
  user
) {
  is_correct <- (runif(1) < 0.5)
  gradethis::graded(
    correct = is_correct,
    message = ifelse(is_correct, correct, incorrect)
  )
}
fifty_fifty_checker()
```

### 

See `?graded` for more information.
