---
title: "Grading demo"
output: learnr::tutorial
runtime: shiny_prerendered
# editor_options:
#   preview: viewer
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)

tutorial_options(exercise.timelimit = 60, exercise.checker = grade_learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Grading Types

### Check Exercise Result

`gradethis` can check for the final returned value.
This grading approach does not inspect the code. It only inspects the final result.

See `?grade_result` for more information.

Example code written below:

````markdown
`r ''````{r result, exercise = TRUE}
3
```

`r ''````{r result-hint-1}
"Is it an even number"
```

`r ''````{r result-hint-2}
"Enter an even number below 5"
```

`r ''````{r result-check}
grade_result(
  results(
    result(1, "Custom message for value 1."),
    result(2, "Custom message for value 2.", correct = TRUE),
    result(3, "Custom message for value 3."),
    result(4, "Custom message for value 4.", correct = TRUE)
  )
)
```
````

-----------------------

* Enter an small even number, then click Submit Answer.

```{r result, exercise = TRUE}
3
```

```{r result-hint-1}
"Is it an even number"
```

```{r result-hint-2}
"Enter an even number below 5"
```

```{r result-check}
grade_result(
  result(1, "Custom message for value 1."),
  result(2, "Custom message for value 2.", correct = TRUE),
  result(3, "Custom message for value 3."),
  result(4, "Custom message for value 4.", correct = TRUE)
)
```

### Test Exercise Result

`gradethis` can test against for the final returned value.  This grading approach does not inspect the code. It only inspects the final result.

Writers can include as many testing functions as they would like.  The test functions should accept a single result value to test against.  If any test fails, it should throw an error.  This error message will be returned back to the user by default.  See `?grade_conditions` for more information.

Example code written below:

````markdown
`r ''````{r grade_conditions, exercise = TRUE}
function(x) {
  sqrt(log(x))
}
```

`r ''````{r grade_conditions-hint-1}
"function(x) {
  sqrt(...)
}"
```

`r ''````{r grade_conditions-hint-2}
"function(x) {
  sqrt(log(...))
}"
```

`r ''````{r grade_conditions-check}
grade_conditions(
  tests(
    function(your_answer) {
      checkmate::expect_function(your_answer, args = c("x"))
    },
    test(
      # use a custom error message
      "Make sure your function returns a number!",
      function(your_answer) {
        checkmate::expect_number(your_answer(1))
      }
    ),
    function(your_answer) {
      testthat::expect_equal(your_answer(0), NaN)
    },
    function(your_answer) {
      testthat::expect_equal(your_answer(1:10), sqrt(log(1:10)))
    }
  )
)
```
````

---------------------------


Please make a function in the exercise space below.  It should:

* Take a single `x` argument
* Take the `log` of `x`
* Take the `sqrt` of the logged value.

Then click Submit Answer.

```{r grade_conditions, exercise = TRUE}
function(x) {
  sqrt(log(x))
}
```

```{r grade_conditions-hint-1}
"function(x) {
  sqrt(...)
}"
```

```{r grade_conditions-hint-2}
"function(x) {
  sqrt(log(...))
}"
```

```{r grade_conditions-check}
grade_conditions(
  tests(
    function(your_answer) {
      checkmate::expect_function(your_answer, args = c("x"))
    },
    test(
      # use a custom error message
      "Make sure your function returns a number!",
      function(your_answer) {
        checkmate::expect_number(your_answer(1))
      }
    ),
    function(your_answer) {
      testthat::expect_equal(your_answer(0), NaN)
    },
    function(your_answer) {
      testthat::expect_equal(your_answer(1:10), sqrt(log(1:10)))
    }
  )
)
```


### Check Exercise Code

`gradethis` can test against an exact code match.  This grading approach does not inspect the computed result.

This check method requires a `*-solution` code chunk containing the solution to compare.  Only the last solution expression and last user expression will be matched.

See `?grade_code` for more information.

Example code written below:

````markdown
`r ''````{r strict, exercise = TRUE}
2
```

`r ''````{r strict-hint-1}
"You can take the log with `log()`"
```

`r ''````{r strict-hint-2}
"You can take the square root with `sqrt()`"
```

`r ''````{r strict-solution}
sqrt(log(2))
```

`r ''````{r strict-check}
grade_code("Good job. Don't worry, things will soon get harder.")
```
````

---------------------------

Here is a number. You can do great things with it, like this:

* Take the square root of the log of the number `2`.

Then click Submit Answer.

```{r strict, exercise = TRUE}
2
```

```{r strict-hint-1}
"You can take the log with `log()`"
```

```{r strict-hint-2}
"You can take the square root with `sqrt()`"
```

```{r strict-solution}
sqrt(log(2))
```

```{r strict-check}
grade_code("Good job. Don't worry, things will soon get harder.")
```





## Custom Checking Code

`gradethis` can accept any checking method that returns a `gradethis::result` object.  The example below returns a correct/incorrect answer with 50/50 probability.


````markdown
`r ''````{r custom, exercise = TRUE}
"Flip a coin"
```

`r ''````{r custom-check}
fifty_fifty_checker <- function(
  correct = "Correct!",
  incorrect = "May the odds ever in your favor!",
  ...,
  user
) {
  is_correct <- (runif(1) < 0.5)
  gradethis::result(
    x = user,
    correct = is_correct,
    message = ifelse(is_correct, correct, incorrect)
  )
}
fifty_fifty_checker()
```
````

---------------------------

Are you feeling lucky?

If you are, click Submit Answer.

```{r custom, exercise = TRUE}
"Flip a coin"
```

```{r custom-check}
fifty_fifty_checker <- function(
  correct = "Correct!",
  incorrect = "May the odds ever in your favor!",
  ...,
  user
) {
  is_correct <- (runif(1) < 0.5)
  gradethis::result(
    x = user,
    correct = is_correct,
    message = ifelse(is_correct, correct, incorrect)
  )
}
fifty_fifty_checker()
```
