---
title: "Gradethis demo"
output: learnr::tutorial
runtime: shiny_prerendered
# editor_options:
#   preview: viewer
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)

tutorial_options(exercise.timelimit = 60, exercise.checker = gradethis::grade_learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Grade Exercise Result

`gradethis` can check for the final returned value.
This grading approach does not inspect the code.
It only inspects the final result.

The final result submitted by the "student" is captured with the `.result` value.

See `?grade_result` for more information.

Example code written below:

````markdown
`r ''````{r grade_result, exercise = TRUE}
3
```

`r ''````{r grade_result-hint-1}
"Is it an even number"
```

`r ''````{r grade_result-hint-2}
"Enter an even number below 5"
```

`r ''````{r grade_result-check}
grade_result(
  fail_if(~ identical(.result, 1), "Custom message for value 1."),
  pass_if(~ identical(.result, 2), "Custom message for value 2."),
  fail_if(~ identical(.result, 3), "Custom message for value 3."),
  pass_if(~ identical(.result %% 2, 0) && (.result < 5),
          "Even number below 5")
)
```
````

-----------------------

* Enter an small even number, then click Submit Answer.

```{r grade_result, exercise = TRUE}
3
```

```{r grade_result-hint-1}
"Is it an even number"
```

```{r grade_result-hint-2}
"Enter an even number below 5"
```

```{r grade_result-check}
grade_result(
  fail_if(~ identical(.result, 1), "Custom message for value 1."),
  pass_if(~ identical(.result, 2), "Custom message for value 2."),
  fail_if(~ identical(.result, 3), "Custom message for value 3."),
  pass_if(~ identical(.result %% 2, 0) && (.result < 5),
          "Even number below 5")
)
```

## Grade Exercise Code

`gradethis` can test against an exact code match.
This grading approach does not inspect the computed result.

This check method requires a `*-solution` code chunk containing the solution to compare.
Only the last solution expression and last user expression will be matched.

See `?grade_code` for more information.

Example code written below:

````markdown
`r ''````{r grade_code, exercise = TRUE}
sqrt(exp(3))
```

`r ''```{r grade_code-hint-1}
"You can take the log with `log()`"
```

`r ''```{r grade_code-hint-2}
"You can take the square root with `sqrt()`"
```

`r ''````{r grade_code-solution}
sqrt(log(2))
```

`r ''```{r grade_code-check}
grade_code("Good job. Don't worry, things will soon get harder.")
```
````

<!-- Need this here so the rstudio editor will color code things correctly
```
-->

---------------------------

Here is a number. You can do great things with it, like this:

* Take the square root of the log of the number `2`.

Then click Submit Answer.

```{r grade_code, exercise = TRUE}
sqrt(exp(3))
```

```{r grade_code-hint-1}
"You can take the log with `log()`"
```

```{r grade_code-hint-2}
"You can take the square root with `sqrt()`"
```

```{r grade_code-solution}
sqrt(log(2))
```

```{r grade_code-check}
grade_code("Good job. Don't worry, things will soon get harder.")
```


## Grade Exercise Conditions

`gradethis` can create multiple tests against for the final returned value.
This grading approach does not inspect the code.
It only inspects the final result against all conditions.

This method is analogous to creating unit tests that all need to pass.

See `?grade_conditions` for more information.

Example code written below:

````markdown
`r ''````{r grade_conditions, exercise = TRUE}
function(x) {
  # solution is x + 1L
  x + 1
}
```

`r ''````{r grade_conditions-hint-1}
"Function should add an integer 1"
```

`r ''````{r grade_conditions-hint-2}
"Integers are created by adding a L to the number, e.g., 10L"
```

`r ''````{r grade_conditions-check}
grade_conditions(
  pass_if(~ .result(3) == 4),
  pass_if(~ identical(.result(0), 1)),
  pass_if(~ identical(sapply(1:10, .result), 2:11)),
  pass_if(~ sapply(1:10, .result) == 2:11),
  pass_if(~ all.equal(sapply(1:10, .result), 2:11)),
  pass_if(~ checkmate::test_function(.result, args = c("x")))
)
```
````

---------------------------


Please make a function in the exercise space below.  It should:

* Take a single `x` argument
* Add the integer `1` to the `x` value.

Then click Submit Answer.

```{r grade_conditions, exercise = TRUE}
function(x) {
  # solution is x + 1L
  x + 1
}
```

```{r grade_conditions-hint-1}
"Function should add an integer 1"
```

```{r grade_conditions-hint-2}
"Integers are created by adding a L to the number, e.g., 10L"
```

```{r grade_conditions-check}
grade_conditions(
  pass_if(~ .result(3) == 4),
  pass_if(~ identical(.result(0), 1)),
  pass_if(~ identical(sapply(1:10, .result), 2:11)),
  pass_if(~ sapply(1:10, .result) == 2:11),
  pass_if(~ all.equal(sapply(1:10, .result), 2:11)),
  pass_if(~ checkmate::test_function(.result, args = c("x")))
)
```

## Custom Checking Code

`gradethis` can accept any checking method that returns a `gradethis::graded` object.
The example below returns a correct/incorrect answer with 50/50 probability.


````markdown
`r ''````{r custom, exercise = TRUE}
"Flip a coin"
```

`r ''````{r custom-check}
fifty_fifty_checker <- function(
  correct = "Correct!",
  incorrect = "May the odds ever in your favor!",
  ...,
  user
) {
  is_correct <- (runif(1) < 0.5)
  gradethis::graded(
    correct = is_correct,
    message = ifelse(is_correct, correct, incorrect)
  )
}
fifty_fifty_checker()
```
````

---------------------------

Are you feeling lucky?

If you are, click Submit Answer.

```{r custom, exercise = TRUE}
"Flip a coin"
```

```{r custom-check}
fifty_fifty_checker <- function(
  correct = "Correct!",
  incorrect = "May the odds ever in your favor!",
  ...,
  user
) {
  is_correct <- (runif(1) < 0.5)
  gradethis::graded(
    correct = is_correct,
    message = ifelse(is_correct, correct, incorrect)
  )
}
fifty_fifty_checker()
```
