
---
title: "script checking"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(dplyr)

library(gradethis)
gradethis::gradethis_setup()
```

The `gradethis` package provides two main functions to check student code [learnr](https://rstudio.github.io/learnr/) tutorials. You can use:

1. `grade_this()` to run an expression to that should determine if the _result_ is correct by calling `pass()` or `fail()` at some point.
1. `grade_this_code()` to check that the student's _code_ exactly matches the solution code.

You can also use `grade_this()` to create your own customized checking code.

### Goal

> Note: `gradethis` does not itself calculate a final grade for the student.



### Environment

`grade_this()` has access to more information than the chunk environment.

Extra objects provided by `gradethis`:
* **`.result`**: The last value from evaluating the user's exercise. Same as `learnr`'s `.last_value`
* **`.solution`**: The last value from evaluating the solution code

Extra items of information from `learnr`:
* **`.label`**: Label for exercise chunk
* **`.solution_code`**: Code provided within the "-solution" chunk for the exercise
* **`.user_code`**: Code submitted by the user
* **`.check_code`**: Code provided within the "-check" (or "-code-check") chunk for the exercise
* **`.envir_result`**: The R environment after the execution of user's exercise submission
* **`.evaluate_result`**: The return value from the `evaluate::evaluate` function
* **`.envir_prep`**: A copy of the R environment before the execution of the exercise submission
* **`.last_value`**: The last value from evaluating the user's exercise submission


### (old) Grade Code
```{r barret0-old, exercise = TRUE}
log(sqrt(2))
```
```{r barret0-old-solution}
log(sqrt(3))
```
```{r barret0-old-code-check-out, eval = FALSE}
grade_code()
```
```{r barret0-old-code-check}
grade_code()
```


### (old) Grade Result
```{r barret1-old, exercise = TRUE}
log(sqrt(2))
```

```{r barret1-old-check-out, eval = FALSE}
grade_result(
  pass_if(~ identical(.result, log(sqrt(3)))),
  fail_if(~ identical(.result, log(sqrt(2))), "change the answer"),
  fail_if(~ TRUE)
)
```
```{r barret1-old-check}
grade_result(
  pass_if(~ identical(.result, log(sqrt(3)))),
  fail_if(~ identical(.result, log(sqrt(2))), "change the answer"),
  fail_if(~ TRUE)
)
```



####  Grade code

```{r barret0-gc, exercise = TRUE}
4
```

```{r barret0-gc-solution}
42
```

```{r barret0-gc-check-out, eval = FALSE}
grade_this_code()
```
```{r barret0-gc-check}
grade_this_code()
```


### Script Style

```{r barret0, exercise = TRUE}
2
```

```{r barret0-solution}
4
```

```{r barret0-check-out, eval = FALSE}
expected <- 4

grade_this({

  testthat::expect_type(.result, "double")
  checkmate::expect_numeric(.result, lower = 0, upper = 10)

  if (identical(.result, expected)) pass("equals 4!")
  # pass_if_equal(4, MESSAGE)
  # fail_if_equal(4, MESSAGE)

  # testthat::expect_equal(.result, expected)

  fail("{random_encourage()}{maybe_code_feedback()}")
})
```
```{r barret0-check}
expected <- 4

grade_this({

  testthat::expect_type(.result, "double")
  checkmate::expect_numeric(.result, lower = 0, upper = 10)

  if (identical(.result, expected)) pass("equals 4!")
  # pass_if_equal(4, MESSAGE)
  # fail_if_equal(4, MESSAGE)

  # testthat::expect_equal(.result, expected)

  fail("{random_encourage()}{maybe_code_feedback()}")
})
```
