---
title: "grade_code messages"
output: 
  html_document:
    toc: true
description: "This tutorial demonstrates how gradethis' grade_code() function provides formative feedback for a variety of common code errors."
---

```{r setup, echo = FALSE}
library(gradethis)
library(glue)
knitr::opts_chunk$set(echo = FALSE)
```

The `grade_code()` function tackles one of the hardest problems in automated learning, which is how to tell students:

1. Which part of their code is wrong, and 
2. How they should fix it

`grade_code()` does this in an automated fashion. It compares the code that a student submits for a learnr exercise to the code that a teacher provides in the exercise's solution chunk. If the two match, `grade_code()` deems the code correct (which is signified by a `NULL` in the feedback messages below). If `grade_code()` spots a difference between the student code and the solution code, `grade_code()` tells the student where their code first diverges and how they should get back on the right track.

The examples below show the feedback messages that `grade_code()` will provide for common coding mistakes.

## Wrong Calls

```{r echo = TRUE}
a <- function(x) x
b <- function(x) x
f <- function(x, y) x + y
g <- function(x, y = a(1)) x + y
```


```{r}
solution <- quote(a(1))
user <- quote(b(1))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a())
user <- quote(a)
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a(1))
user <- quote(b(a(1)))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a(1))
user <- quote(a(b(1)))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:

```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a(1))
user <- quote(a(a(1)))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a(1))
user <- quote(0 + a(1))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a(1))
user <- quote(a(1) + 0)
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a() + a())
user <- quote(a() + b())
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a() + a())
user <- quote(b() + a())
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a(b(1)))
user <- quote(b(1) %>% a())
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
# NULL implies the code was deemed correct
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a(b(1)))
user <- quote(a(1) %>% b())
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a(a(1)))
user <- quote(b(1) %>% a())
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(b(b(1)))
user <- quote(b(1) %>% a())
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(f(1, y = a(1)))
user <- quote(f(1, y = b(1)))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(f(1, y = a(1)))
user <- quote(f(1, y = b(a(1))))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(f(1, y = a(1)))
user <- quote(f(1, y = a(b(1))))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```


***

```{r}
solution <- quote(f(1, y = a(1)))
user <- quote(f(1, y = b(b(1))))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(f(1, y = a(1)))
user <- quote(f(1, y = a(a(1))))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

```{r}
solution <- quote(g(1)) # default y = a(1)
user <- quote(g(1, y = a(1)))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(g(1)) # default y = a(1)
user <- quote(g(1, y = b(1)))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(f(1, y = a(1)))
user <- quote(f(1, y = f(1)))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***


# Wrong values

```{r echo = TRUE}
a <- function(x) x
b <- function(x) x
x <- 1
y <- 1
X <- 1
```

***

```{r}
solution <- quote(1)
user <- quote(2)
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(1)
user <- quote(-1)
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(1)
user <- quote(1L)
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(1)
user <- quote(1())
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```


***

```{r}
solution <- quote(x)
user <- quote(y)
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(x)
user <- quote(X)
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a(1))
user <- quote(a(2))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a(1))
user <- quote(a(-1))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a(1))
user <- quote(a(1L))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a(x))
user <- quote(a(y))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a(x))
user <- quote(a(X))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

```{r}
solution <- quote(1 + 2)
user <- quote(1 + 1)
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(1 + 2)
user <- quote(2 + 1)
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(1 %>% f(2))
user <- quote(3 %>% f(2))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(1 %>% f(2))
user <- quote(1 %>% f(3))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

# Bad Argument Names

```{r echo = TRUE}
# the name a will fail to uniquely match
tricky <- function(aa = 1, ab = 2, ac = 3) aa
```

***

```{r}
solution <- quote(tricky(ab = 1))
user <- quote(tricky(a = 1))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(tricky(ab = 1))
user <- quote(tricky(1, 2, a = 1))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(tricky(ab = 1))
user <- quote(1 %>% tricky(a = 2))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(tricky(ab = 1))
user <- quote(1 %>% tricky(a = .))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

# Formal argument name matches too many provided names

```{r echo = TRUE}
# What if multiple arguments partially match ambiguous?
tricky2 <- function(ambiguous = 1, ...) ambiguous
not_tricky <- function(a = 1, ambiguous = 2, ...) a
```

***

```{r}
solution <- quote(tricky2(amb = 2))
user <- quote(tricky2(a = 2, am = 2))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(not_tricky(amb = 2))
user <- quote(not_tricky(a = 1, am = 2))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(tricky2(amb = 2))
user <- quote(2 %>% tricky2(a = ., am = 2))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

# Surplus Arguments

```{r echo = TRUE}
h <- function(x) x
i <- function(x, ...) x
```

***

```{r}
solution <- quote(h(x = 1))
user <- quote(h(x = 1, y = 2))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(h(x = 1))
user <- quote(h(1, 2))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(i(x = 1))
user <- quote(i(1, 2))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(i(x = 1))
user <- quote(i(1, x = 2))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(h(x = 1))
user <- quote(1 %>% h(2))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

# Missing Arguments

```{r echo = TRUE}
f <- function(x, y) x + y
g <- function(x, y = a(1)) x + y
z <- function(...) 1
```

***

```{r}
solution <- quote(f(x = 1, y = 1))
user <- quote(f(x = 1))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a(f(x = 1, y = 2)))
user <- quote(a(f(x = 1)))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(f(x = 1, y = 2))
user <- quote(f(y = 2))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(f(x = 1, y = 2))
user <- quote(f(1))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(f(x = 1, y = 2))
user <- quote(1 %>% f())
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a(f(x = 1, y = 2)))
user <- quote(a(1 %>% f()))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(a(1))
user <- quote(a())
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(z(1))
user <- quote(z())
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

```{r}
solution <- quote(z(a(1)))
user <- quote(z())
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***

# Duplicate names

```{r echo = TRUE}
i <- function(x, ...) x
```

***

```{r}
solution <- quote(i(x = 1))
user <- quote(i(x = 1, x = 2))
```

Correct: ``r gradethis:::deparse_to_string(solution)``  
Student: ``r gradethis:::deparse_to_string(user)``  
Feedback:
```{r echo = FALSE}
gradethis:::detect_mistakes(user, solution)
```

***
