
### Always debug

The first method is the most straight-forward. 
Inside the `*-check` or `*-error-check` chunks for your exercise,
simply call `debug_this()`:

````
```{r example-check}`r ''`
debug_this()
```
````

Every time you submit code for feedback via **Submit Answer**,
the debug information will be printed.


### Debug specific cases

On the other hand, if you want to debug a specific submission,
such as a case where a submission isn't matching any of your current grading conditions,
you can call `debug_this()` wherever you like inside [grade_this()].

````
```{r example-check}`r ''`
grade_this({
  pass_if_equal(3, "Good work?")
  
  # debug the submission if it is somehow equal to 2
  if (.result == 2) {
    debug_this()
  }
})
```
````

### Debug default fail condition

It's common to have the grade-checking code 
default to an incorrect grade with code feedback
by calling `fail()` at the end of the checking code in [grade_this()].
During development of a tutorial,
you may want to have this default `fail()` return the debugging information
rather than a failure.

By setting the global option `gradethis.fail` to use `debug_this()`,

````
```{r setup}`r ''`
library(learnr)
library(gradethis)
gradethis_setup()

option(gradethis.fail = "{debug_this()}")
```
````

you can see the values that are available to you during the submission check
whenever your test submissions pass through your other checks.

````
```{r example-check}`r ''`
grade_this({
  pass_if_equal(3, "Good work?")
  
  fail()
})
```
````

Don't forget to reset or unset the `gradethis.fail` option
when you're done working on your tutorial.
